Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-24 paper/paper.tex
commented out sagan footnote for now. preflight footnotes in-line.

We also wanted to balance building with buying, keeping in mind our slim finances. While its impossible to truly start from scratch\footnote{``If you want to make an apple pie from scratch, you must first create the universe'' - Dr. Carl Sagan \cite{saganquote}}, we tried to build whatever we could given the 16th June competition deadline.

% footnote is broken (breaks from bottom of page one onto bottom of page two), something about the documentclass needs to be changed so it doesn't assume pages are next to each other (book-like)?

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Preflight Procedures}
\label{sec:appendix_preflight}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extensions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnotemark, centerman\footnotemark.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``receiver on''.  Centerman turns on receiver, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

@@

\footnotetext[1]{Two men, one positioned at each wing tip, preventing the plane from moving during engine start and subsequent surface checks.}
\footnotetext{Man straddling the fuse, preventing the plane from moving during engine start and subsequent surface checks}

>>>>

We also wanted to balance building with buying, keeping in mind our slim finances. While we couldn't build every part of our entry from scratch, we tried to build whatever we could given the 16th June competition deadline.

%\footnote{``If you want to make an apple pie from scratch, you must first create the universe'' - Dr. Carl Sagan \cite{saganquote}},

@@

\subsection{Safety Observers}
A safety observer is defined as a person, devoid of any additional specific responsibilities, who remains in the starting area during all pre-flight procedures.  The safety observer is expected to watch for unsafe conditions, included but not limited to non-essential personnel in the starting, takeoff, and/or flight areas; loose mechanical connections; failed surface and/or range checks; and other forms of mechanical failure.  The safety observer has the absolute authority to give the order to kill the ignition and abort startup immediately upon observing any unsafe condition.  The safety observer is responsible for communicating possible conditions to the startup team as they arise. At minimum, one safety observer is required to start the engine, though we typically have more.

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Preflight Procedures}
\label{sec:appendix_preflight}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extensions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnote{Two men, one positioned at each wing tip, preventing the plane from moving during engine start and subsequent surface checks.}, centerman\footnote{Man straddling the fuse, preventing the plane from moving during engine start and subsequent surface checks}.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``receiver on''.  Centerman turns on receiver, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

@@
